The Unintended Consequences of Energy Reduction

### 2024-02-15 other/ssrp/ssrp_report.qmd
Minor edit tod authors

---
title: "SSRP Report based on *Energy Saving May Kill: Evidence from the Fukushima Nuclear Accident* by He and Tanaka (2019)"
author:
  - Yi Fei Pang
  - Irene Hyunh
  - Tara Chakkithara
thanks: "Code and data are available at: https://github.com/apang00/Energy-Policy.git"
date: today
date-format: long
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "SSRP Report based on *Energy Saving May Kill: Evidence from the Fukushima Nuclear Accident* by He and Tanaka (2019)"
author:
  - Yi Fei Pang
  - Irene Huynh
  - Tara Chakkithara
thanks: "Code and data are available at: https://github.com/apang00/Energy-Policy.git"
date: today
date-format: long
format: pdf
number-sections: true
bibliography: references.bib
---

### 2024-02-15 paper/paper.qmd
Minor edit tod authors

---
title: "The Unintended Consequences of Energy Reduction"
subtitle: "How an Act of Environmental Protection Led to the Deaths of Many"
author:
  - Yi Fei Pang
  - Irene Hyunh
  - Tara Chakkithara
thanks: "Code and data are available at: https://github.com/apang00/Energy-Policy.git"
date: today
date-format: long
abstract: "Nuclear energy is a clean power source that produces electricity while operating with low-carbon emissions. Although nuclear power generation has its advantages, many concerns have been raised regarding its safety after the Fukushima nuclear accident of 2011. This paper analyzes the utilization of nuclear energy, the price of electricity and electricity consumption, and the temperature-mortality relationship in Japan before and after the accident. We reveal that the use of nuclear energy in Japan sharply decreased following the nuclear accident, resulting in a power shortage scare and surge in electricity prices across Japan. This prompted the country’s government to push an energy saving mindset to the public, and as a result, electricity consumption plummeted. However, we find that the government’s efforts created adverse effects as days with high temperatures coupled with an energy saving mindset led to a higher mortality rate and a shift to fossil fuel dependent energy poses grave consequences to the environment. These findings prompt discussions about the true cost of energy saving."
pdf-engine: pdflatex
format:
  pdf:
    documentclass: article
    geometry:
      - top=30mm
      - left=20mm
      - heightrounded
include: false
warning: false
message: false
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "The Unintended Consequences of Energy Reduction"
subtitle: "How an Act of Environmental Protection Led to the Deaths of Many"
author:
  - Yi Fei Pang
  - Irene Huynh
  - Tara Chakkithara
thanks: "Code and data are available at: https://github.com/apang00/Energy-Policy.git"
date: today
date-format: long
abstract: "Nuclear energy is a clean power source that produces electricity while operating with low-carbon emissions. Although nuclear power generation has its advantages, many concerns have been raised regarding its safety after the Fukushima nuclear accident of 2011. This paper analyzes the utilization of nuclear energy, the price of electricity and electricity consumption, and the temperature-mortality relationship in Japan before and after the accident. We reveal that the use of nuclear energy in Japan sharply decreased following the nuclear accident, resulting in a power shortage scare and surge in electricity prices across Japan. This prompted the country’s government to push an energy saving mindset to the public, and as a result, electricity consumption plummeted. However, we find that the government’s efforts created adverse effects as days with high temperatures coupled with an energy saving mindset led to a higher mortality rate and a shift to fossil fuel dependent energy poses grave consequences to the environment. These findings prompt discussions about the true cost of energy saving."
pdf-engine: pdflatex
format:
  pdf:
    documentclass: article
    geometry:
      - top=30mm
      - left=20mm
      - heightrounded
include: false
warning: false
message: false
number-sections: true
bibliography: references.bib
---
